\section{Related Work} \label{sec:related work}

Important early work in real time scheduling by Liu and Layland~\cite{Liu73} presented two classic scheduling algorithms, rate-monotonic priority assignment and deadline-driven scheduling, 
and assessed their performance based on processor utilization. Their work, however, does not consider energy constraints. 
Moser \emph{et al.}~\cite{moser2007real}, in more recent work, described energy-aware \textsc{lsa} scheduling
and proved that it optimally deals with time and energy constraints in a system whose energy storage is replenished \textit{predictably}. 
The suitability of this approach under realistic energy harvesting conditions, however, is unclear. 

Research into energy-aware algorithms for sensor nodes is an active area. 
Power management algorithms based on duty-cycling between active and low-power modes of sensor nodes 
with energy harvesting capabilities have been 
presented by Kansal \emph{et al.}~\cite{kansal2007power}. 
Niyato \emph{et al.}~\cite{niyato2007sleep} investigated the impact of different sleep and wake-up strategies on data communication
among solar-powered nodes. 
In~\cite{vigorito2007adaptive}, Vigorito \emph{et al.} proposed an adaptive duty-cycling algorithm that ensures 
that power supplied to sensor nodes is kept within operational levels regardless of changing environmental conditions. 
In~\cite{moser2007adaptive}, Moser \emph{et al.} presented an adaptive power management
model that can be customized to address different constraints and optimization objectives in energy harvesting systems.

Predicting stochastic energy sources is non-trivial.  
Lu \emph{et al.}~\cite{lu2010accurate} assessed three prediction techniques for real-time systems: regression analysis,
moving average, and exponential smoothing. Recas~\emph{et al.}~\cite{recas2000hollows} employed the Weather-Conditioned Moving Average (\textsc{wcma}) model, which adapts to seasonal changes in
solar power harvesting as well as sudden weather changes. 
Moser \emph{et al.}~\cite{moser2007real} introduced energy variability curves to predict the power provided by a 
harvesting unit. 
In~\cite{susu2008stochastic} Susu \emph{et al.} used a discrete-time Markov chain in which only transitions between 
consecutive states, representing energy levels, were allowed. 
On the other hand, Niyato \emph{et al.}~\cite{niyato2007sleep} made use of a Markov chain model that takes into consideration the influence of clouds and wind on solar radiation intensity. 
Due to the limited computational and memory resources available on a typical sensor node, however,
implementing suitably accurate dynamic energy predication models appears challenging, making 
scheduling algorithms based on energy predication impractical. 

%The majority of energy harvesting systems are based on rechargeable batteries, as noted by Sudevalayam and Kulkarni~\cite{sudevalyam2010energy}.
%However, Simjee and Chou~\cite{simjee2007everlast} add that there has been increasing interest in %supercapacitors, which theoretically have infinite charge cycles and high power densities. In~\cite{jiang2005perpetual}, Jiang \emph{et. al.} present a hybrid implementation based on two supercapacitors and one rechargeable battery.
